POMDP comparisons across sigma_m, sigma_g

### 2017-10-04 appendix/appendixB.Rmd
fewer cores

```{r aethetics, include=FALSE}
library(printr)
knitr::opts_chunk$set(message=FALSE, comment="")
```

@@

```{r}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
options(mc.cores = 6) # Reserve ~ 10 GB per core
log_dir <- "pomdp_intro"
```

>>>>

```{r aethetics, include=FALSE}
#library(printr)
knitr::opts_chunk$set(message=FALSE, comment="")
```

@@

```{r}
# devtools::install_github("boettiger-lab/sarsop")  ## install package first if necessary.
library(sarsop)       # the main POMDP package
library(tidyverse)    # for munging and plotting
library(parallel)
options(mc.cores = 3) # Reserve ~ 10 GB per core
log_dir <- "pomdp_intro"
```
